The Units of Permissionless Consensus: \\ Towards Mobile and Edge Computing

### 2022-11-17 theoretical-consensus/article/article.tex
add readme

This paper presents an overview of the consensus problem
applicable to permissionless environments. Starting from 
the classical roots of consensus in distributed systems,
and then transitioning to the more recent developments in the
field of permissionless consensus, this paper also reviews
the common approaches and architectural design of the most well known protocols, 
and discusses the trade-offs between the different approaches.
Finally, this paper points out the challenges that
permissionless consensus faces in the context of resource
constrained environments, such as mobile and edge computing,
identifies and argues about the current approaches to address these challenges,
and shows potential research directions.

@@

As pointed out by \cite{xiao2019distributed, 8629877} and then referenced by \cite{survey-dist-consensus}, 
similarly to the permissioned counterparts, permissionless consensus protocols 
aim at achieving the following properties: Termination, Agreement, Validity, 
and Integrity. Without going into a lot of details, of these properties, 
Agreement and Integrity are the most important ones, as they are the ones that
guarantee the correctness of the consensus protocols. Termination and Validity
are generally related to any classic consensus problem.

>>>>

This paper presents an overview of the consensus problem
applicable to permissionless environments. Starting from 
the classical roots of consensus in distributed systems,
transitioning to the more recent developments in the
field of permissionless consensus, this paper also reviews
the common approaches and architectural design of the most well known protocols, 
and discusses the trade-offs between the different approaches.
Finally, this paper points out the challenges that
permissionless consensus faces in the context of resource
constrained environments, such as mobile and edge computing.
It identifies and argues about the current approaches to address these challenges,
and shows potential research directions.

@@

As pointed out by \cite{xiao2019distributed, 8629877} and then referenced by \cite{survey-dist-consensus}, 
similarly to the permissioned counterparts, permissionless consensus protocols 
aim at achieving the following properties: Termination, Agreement, Validity, 
and Integrity. Without going into a lot of details, of these properties, 
Agreement and Integrity are the most important ones, as they are the ones that
guarantee the correctness of the consensus protocols. Termination and Validity
are generally related to any classical consensus problem.
